Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-04 manuscript/main.tex
updated numbers in section cfx in gaze

Next, we tested whether participants' eye movements were affected by the set of available alternatives, similar to their choices. We therefore computed each alternative's relative dwell time in a trial by summing the duration of all fixations durations towards it, and normalizing to the sum of all fixations in the trial. Both patterns of context effects of choice behaviour were present in the relative dwell data: Target options received greater relative dwell time than competitors in attraction (mean difference = 0.015, HDI$_{95}$ = [0.005, 0.4], mean $d$ = 0.55, HDI$_{95}$  = [0.16, 0.98], Figure \ref{fig:cfx}c) and compromise trials (mean difference = 0.022, HDI$_{95}$  = [0.014, 0.03], mean $d$ = 0.91, HDI$_{95}$  = [0.53, 1.28], Figure \ref{fig:cfx}f). Targets and competitors also received greater relative dwell time than decoys in both trial types.

>>>>

Next, we tested whether participants' eye movements were affected by the set of available alternatives, similar to their choices. We therefore computed each alternative's relative dwell time in a trial by summing the duration of all fixations durations towards it, and normalizing to the sum of all fixations in the trial. Both patterns of context effects of choice behaviour were present in the relative dwell data: Target options received greater relative dwell time than competitors in attraction (mean difference = 0.014, HDI$_{95}$ = [0.004, 0.024], mean $d$ = 0.53, HDI$_{95}$  = [0.15, 0.93], Figure \ref{fig:cfx}c) and compromise trials (mean difference = 0.022, HDI$_{95}$  = [0.014, 0.030], mean $d$ = 0.90, HDI$_{95}$  = [0.53, 1.31], Figure \ref{fig:cfx}f). Targets and competitors also received greater relative dwell time than decoys in both trial types.
